---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

## Drink orders in some cafes in Auckland
```{r data}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTHiKwjLs8KixSKd4urABaRFwlwWwBJn9-3jQihVOYn4b45k-qvKAk0-Cy39RJ_LPho4g2ThHOtW9_j/pub?gid=1648384591&single=true&output=csv")

```

### Two summary functions
I have decided to capture the most amount of drinks in one order, as I think this would intriguing to see. Next I have produced the mean activity level of all cafes in the data set and described the numeric activity level in words.


```{r summary functions}
latest_data <-logged_data %>% 
rename (drink_type = 2, number_drinks = 3, surburb_cafe = 4,
        levelofbusycafe = 5, timeoforder = 6) 

paste("The highest number of drinks ordered in one go is", max(latest_data$number_drinks))

paste("The mean level of activity in a cafe is", round((sum(latest_data$levelofbusycafe))/21,2), 
      ". This means that on average cafes were fairly busy with some seats filled", collapse = "")
```

### Two bar plots
The first plot displays the location of the cafes I frequented in recording this data. The second plot am captures the count of each type of drink that was ordered over the time period the data was collected.


```{r bar plots}
latest_data %>% 
  ggplot() + 
    geom_bar(aes(x = surburb_cafe, fill = surburb_cafe)) + 
  scale_fill_manual(values=c("#96b085", "#82b8c2", "#9d83a6", "#ee9e3d")) +
  labs(title = "Auckland surburbs drinks were ordered from",
       x = "Number of cafes", y = "Location of cafe")

typedrink <- latest_data %>% separate_rows(drink_type, sep = ", ")
typedrink %>% 
  ggplot()+
    geom_bar(aes(y = drink_type, fill = drink_type)) +
  scale_fill_manual(values=c("#67390a", "#a47551", "#ffb365", "#fdacab", "#c8e397", "#e5cdae")) +
  labs(title = "Types of drinks ordered",
       subtitle = "In some Auckland cafes",
       x = "Total number of drinks", y = "Type of drink") 
```

